Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core

### 2006-04-11 BD_radvel/kurosawa.tex
Dates (MDJ -> HJD) changed. Observed dates were 1 day off (I was listing the dates the data was reduced before instead)...=> fixed. (RK).
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@704 25464f21-6099-402c-b30a-640f1d40d38b

We obtained high-resolution spectra with the Kueyen telescope of VLT
(Cerro Parnal, Chile) using the UVES echelle spectrograph. The observations
were carried out between 2004 April 5 and 2005 (XXX?)  May 15 in  service
mode. For each object, spectra were obtained at two different
epochs separated by several (between 4 and 33~d). For each object at a given 
night, two separate spectra are obtained consecutively. This allows us to derive more
reliable uncertainty estimates in the RV values of our targets (c.f.~\citealt{joergens:2006}).
The data were obtained using the red arm of UVES spectrograph with
two mosaic CCDs (EEV + MIT/LL with 2k$\times$4k pixels). The wavelength
coverage of 6708 -- 10,250~\AA\, and the spectral resolution $R\approx40,000$
were used. The slit width and length of 1'' and 12'' were used respectively with a typical seeing
of 0.8''.

@@

\begin{tabular}{lcrrrrrc}
\hline 
Object&
Date&
MDJ-2453100&
RV&
$\sigma_{\mathrm{RRV}}$&
$\overline{\mathrm{RV}}$&
$v\sin i$&
candidate?\tabularnewline
&
&
&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
\tabularnewline
\hline 
GY 5&
2004-Apr-25&
20.22051&
$-6.14\pm0.84$&
0.68&
&
&
\tabularnewline
&
2004-May-08&
33.27776&
$-5.96\pm0.60$&
0.34&
$-6.05\pm1.03$&
$16.5\pm0.6$&
no\tabularnewline
GY 141&
2004-May-11&
36.16016&
$-4.39\pm0.60$&
0.34&
&
&
\tabularnewline
&
2004-May-18&
43.15707&
$-2.95\pm0.51$&
0.11&
$-3.67\pm0.79$&
$4.4\pm1.4$&
yes\tabularnewline
GY 310&
2004-Apr-25&
20.32700&
$-4.83\pm0.74$&
0.54&
&
&
\tabularnewline
&
2004-May-10&
35.31139&
$-8.43\pm0.51$&
0.11&
$-6.63\pm0.90$&
$11.1\pm6.0$&
yes\tabularnewline
USco 40&
2004-Apr-06&
01.25900&
$-7.15\pm0.74$&
0.54&
&
&
\tabularnewline
&
2004-May-08&
33.25324&
$-6.80\pm0.51$&
0.11&
$-6.98\pm0.90$&
$34.2\pm0.5$&
no\tabularnewline
USco 53&
2004-Apr-05&
00.39651&
$-7.27\pm0.93$&
1.21&
&
&
\tabularnewline
&
2004-May-03&
28.23079&
$-5.43\pm0.74$&
0.55&
$-6.35\pm1.19$&
$40.0\pm0.6$&
no\tabularnewline
USco 55&
2004-Apr-06&
01.33509&
$-5.39\pm0.50$&
0.02&
&
&
\tabularnewline
&
2004-May-03&
28.30546&
$-6.38\pm0.53$&
0.27&
$-6.38\pm0.73$&
$22.9\pm0.8$&
yes\tabularnewline
USco 66&
2004-Apr-06&
01.29007&
$-5.32\pm0.57$&
0.29&
&
&
\tabularnewline
&
2004-May-03&
28.28683&
$-6.41\pm0.65$&
0.42&
$-5.87\pm0.86$&
$25.9\pm1.2$&
no\tabularnewline
USco 67&
2004-Apr-06&
01.21481&
$-6.01\pm0.74$&
0.55&
&
&
\tabularnewline
&
2004-May-03&
28.21759&
$-6.83\pm0.59$&
0.31&
$-6.42\pm0.90$&
$18.4\pm0.4$&
no\tabularnewline
USco 75&
2004-Apr-05&
00.37453&
$-6.75\pm0.67$&
0.44&
&
&
\tabularnewline
&
2004-May-08&
33.09532&
$-9.88\pm1.94$&
1.88&
$-8.32\pm2.05$&
$55.6\pm3.0$&
yes\tabularnewline
USco 100&
2004-Apr-06&
01.30836&
$-6.76\pm2.74$&
2.69&
&
&
\tabularnewline
&
2004-May-03&
28.26425&
$-10.23\pm1.80$&
1.73&
$-8.47\pm3.28$&
$43.7\pm3.2$&
no\tabularnewline
USco 101&
2004-Apr-05&
00.30191&
$-4.22\pm0.87$&
0.71&
&
&
\tabularnewline
&
2004-May-03&
28.14804&
$-6.07\pm0.69$&
0.48&
$-5.15\pm1.11$&
$19.1\pm0.3$&
yes\tabularnewline
USco 104&
2004-Apr-05&
00.27545&
$-5.83\pm0.50$&
0.02&
&
&
\tabularnewline
&
2004-May-03&
28.12391&
$-7.48\pm0.50$&
0.06&
$-6.66\pm0.06$&
$16.7\pm0.4$&
yes\tabularnewline
USco 109&
2004-Apr-06&
01.23587&
$-4.15\pm0.52$&
0.16&
&
&
\tabularnewline
&
2004-May-08&
33.11929&
$-4.41\pm0.50$&
0.03&
$-5.12\pm0.72$&
$8.6\pm1.2$&
yes\tabularnewline
USco 112&
2004-Apr-05&
00.34486&
$-2.70\pm0.69$&
0.47&
&
&
\tabularnewline
&
2004-May-08&
33.07139&
$-3.46\pm0.51$&
0.11&
$-3.08\pm0.86$&
$5.8\pm1.2$&
yes\tabularnewline
USco 121&
2004-Apr-25&
20.19466&
$-39.47\pm0.51$&
0.11&
&
&
\tabularnewline
&
2004-May-03&
28.18537&
$-42.43\pm0.50$&
0.02&
$-40.95\pm0.71$&
$17.6\pm1.3$&
yes\tabularnewline
USco 128&
2004-May-14&
39.28595&
$-7.41\pm0.85$&
0.69&
&
&
\tabularnewline
&
2004-May-18&
43.09885&
$-6.94\pm1.16$&
1.05&
$-7.18\pm1.44$&
$3.6\pm1.1$&
no\tabularnewline
USco 130&
2004-May-10&
35.26060&
$-4.83\pm0.54$&
0.21&
&
&
\tabularnewline
&
2004-May-14&
39.34201&
$-4.95\pm0.74$&
0.55&
$-4.89\pm0.92$&
$15.2\pm1.1$&
no\tabularnewline
USco 132&
2004-May-12&
37.28394&
$-7.18\pm0.58$&
0.30&
&
&
\tabularnewline
&
2004-Jun-18&
43.12719&
$-7.37\pm1.02$&
0.89&
$-7.28\pm1.17$&
$9.1\pm0.7$&
no\tabularnewline
\hline
\end{tabular}

@@

\caption{Relative radial velocities (RVs) of objects measured in two different epochs. The vertical axes indicate  the amount of deviation ($\Delta \mathrm{RV}$) from the `average' radial velocitiy  ($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}), and the horizontal axes indicate the time of the observation in modified Julian date (MJD; XXX do you really mean MJD rather than heliocentric JD????). The objects are considered to have a non-constant  RV when the error bars of two data points do not overlap each other. The non-constant RV objects are considered as binary/multiple candidates.}

@@

The radial velocities of each object were determined by using the cross-correlation
function of the object spectrum with that of a template star which has
a spectra type. By visual inspection,
the wavelength ranges used for the cross-correlation calculations
are chosen by avoiding the regions of spectra affected by the telluric
lines, and defects and fringes (in near infrared) of the CCDs. The
radial velocities of objects with respect to the template are obtained
by measuring the location of the peak in the cross-correlation function
which is fitted by the combination of two gaussian functions sharing
their centres and a constant term (XXXX What does this mean?). LHS~49 (Proxima Cen, M5.5) was
chosen as the template for this purpose. The radial velocity of the
template object LHS~49 was obtained by measuring the wavelength shifts
of the prominent photospheric absorption features \ion{K}{i}~$\lambda\lambda$7664.911,~7698.974.
This gives us $\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$, which is
in good agreement with the earlier measurement of \citet{garcia-sanchez:2001}
who found $\mathrm{RV_{LHS49}=}-21.7\pm1.8\,\kmps$. The heliocentric
RV of each object can be then calculated by adding $\mathrm{RV_{LHS49}}$
with the RV of each object with respect to LHS~49. In the following
measurements of the heliocentric radial velocities, our measurement
($\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$) will be used for consistency.

@@

The result of the heliocentric RV measurements (from two epochs for
each object) is summarised in Table~\ref{tab:summary_results} along
with the uncertainties. The table also lists the uncertainties in
the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
is the uncertainty of RV with respect to the template star. The
two consecutive measurements of RVs (from same nights) are used to
find the RV of the night, and their uncertainties are obtained from
the standard deviations of the mean ($\sigma_{\mathrm{RRV}}$) and
the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
(XXX What do you need to include the uncertainty in the template
star measurement when we are looking for relative changes in the
bd RVs?) The 'average' radial velocities ($\overline{\mathrm{RV}}$) of the
two epochs are also given in the same table. The $\overline{\mathrm{RV}}$
values of the objects in UScoOB are consistent with the earlier measurements
of \citet{muzerolle:2003} in Table~\ref{tab:literatures}, except
for the values for USco~66 and USco~75. This is unsurprising
since the former is a known binary \citep{kraus:2005} and the latter
is a non-constant RV object (a candidate for a multiple) found in
the RV-shift test which will be discussed next.

@@

This work is supported by PPARC rolling grant PP/C501609/1. We thank
the staff of VLT of the ESO for the observations carried out in
service mode.

>>>>

We obtained high-resolution spectra with the Kueyen telescope of VLT
(Cerro Parnal, Chile) using the UVES echelle spectrograph. The observations
were carried out between 2004 April 5 and 2004 May 17 in  service
mode. For each object, spectra were obtained at two different
epochs separated by several (between 4 and 33~d). For each object at a given 
night, two separate spectra are obtained consecutively. This allows us to derive more
reliable uncertainty estimates in the RV values of our targets (c.f.~\citealt{joergens:2006}).
The data were obtained using the red arm of UVES spectrograph with
two mosaic CCDs (EEV + MIT/LL with 2k$\times$4k pixels). The wavelength
coverage of 6708 -- 10,250~\AA\, and the spectral resolution $R\approx40,000$
were used. The slit width and length of 1'' and 12'' were used respectively with a typical seeing
of 0.8''.

@@

\begin{tabular}{lcrrrrrc}
\hline 
Object&
Date&
HJD-2453100&
RV&
$\sigma_{\mathrm{RRV}}$&
$\overline{\mathrm{RV}}$&
$v\sin i$&
candidate?\tabularnewline
&
&
&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
\tabularnewline
\hline 
GY 5&
2004-Apr-24&
20.7198440&
$-6.14\pm0.84$&
0.68&
&
&
\tabularnewline
&
2004-May-07&
33.7721938&
$-5.96\pm0.60$&
0.34&
$-6.05\pm1.03$&
$16.5\pm0.6$&
no\tabularnewline
GY 141&
2004-May-10&
36.6712108&
$-4.39\pm0.60$&
0.34&
&
&
\tabularnewline
&
2004-May-17&
43.6683007&
$-2.95\pm0.51$&
0.11&
$-3.67\pm0.79$&
$4.4\pm1.4$&
yes\tabularnewline
GY 310&
2004-Apr-24&
20.8373504&
$-4.83\pm0.74$&
0.54&
&
&
\tabularnewline
&
2004-May-09&
35.8224052&
$-8.43\pm0.51$&
0.11&
$-6.63\pm0.90$&
$11.1\pm6.0$&
yes\tabularnewline
USco 40&
2004-Apr-05&
1.7661754&
$-7.15\pm0.74$&
0.54&
&
&
\tabularnewline
&
2004-May-07&
33.7620554&
$-6.80\pm0.51$&
0.11&
$-6.98\pm0.90$&
$34.2\pm0.5$&
no\tabularnewline
USco 53&
2004-Apr-04&
0.9036653&
$-7.27\pm0.93$&
1.21&
&
&
\tabularnewline
&
2004-May-02&
28.7394676&
$-5.43\pm0.74$&
0.55&
$-6.35\pm1.19$&
$40.0\pm0.6$&
no\tabularnewline
USco 55&
2004-Apr-05&
1.8422807&
$-5.39\pm0.50$&
0.02&
&
&
\tabularnewline
&
2004-May-02&
28.8141198&
$-6.38\pm0.53$&
0.27&
$-6.38\pm0.73$&
$22.9\pm0.8$&
yes\tabularnewline
USco 66&
2004-Apr-05&
1.7972634&
$-5.32\pm0.57$&
0.29&
&
&
\tabularnewline
&
2004-May-02&
28.7956003&
$-6.41\pm0.65$&
0.42&
$-5.87\pm0.86$&
$25.9\pm1.2$&
no\tabularnewline
USco 67&
2004-Apr-05&
1.7188620&
$-6.01\pm0.74$&
0.55&
&
&
\tabularnewline
&
2004-May-02&
28.7113799&
$-6.83\pm0.59$&
0.31&
$-6.42\pm0.90$&
$18.4\pm0.4$&
no\tabularnewline
USco 75&
2004-Apr-04&
0.8840376&
$-6.75\pm0.67$&
0.44&
&
&
\tabularnewline
&
2004-May-07&
33.6065432&
$-9.88\pm1.94$&
1.88&
$-8.32\pm2.05$&
$55.6\pm3.0$&
yes\tabularnewline
USco 100&
2004-Apr-06&
1.8179138&
$-6.76\pm2.74$&
2.69&
&
&
\tabularnewline
&
2004-May-02&
28.7752928&
$-10.23\pm1.80$&
1.73&
$-8.47\pm3.28$&
$43.7\pm3.2$&
no\tabularnewline
USco 101&
2004-Apr-04&
0.8120734&
$-4.22\pm0.87$&
0.71&
&
&
\tabularnewline
&
2004-May-02&
28.6591660&
$-6.07\pm0.69$&
0.48&
$-5.15\pm1.11$&
$19.1\pm0.3$&
yes\tabularnewline
USco 104&
2004-Apr-04&
0.7850385&
$-5.83\pm0.50$&
0.02&
&
&
\tabularnewline
&
2004-May-02&
28.6349480&
$-7.48\pm0.50$&
0.06&
$-6.66\pm0.06$&
$16.7\pm0.4$&
yes\tabularnewline
USco 109&
2004-Apr-05&
1.7453989&
$-4.15\pm0.52$&
0.16&
&
&
\tabularnewline
&
2004-May-07&
33.6304878&
$-4.41\pm0.50$&
0.03&
$-5.12\pm0.72$&
$8.6\pm1.2$&
yes\tabularnewline
USco 112&
2004-Apr-04&
0.8552168&
$-2.70\pm0.69$&
0.47&
&
&
\tabularnewline
&
2004-May-07&
33.5826368&
$-3.46\pm0.51$&
0.11&
$-3.08\pm0.86$&
$5.8\pm1.2$&
yes\tabularnewline
USco 121&
2004-Apr-24&
20.7059408&
$-39.47\pm0.51$&
0.11&
&
&
\tabularnewline
&
2004-May-02&
28.6969641&
$-42.43\pm0.50$&
0.02&
$-40.95\pm0.71$&
$17.6\pm1.3$&
yes\tabularnewline
USco 128&
2004-May-13&
39.7978276&
$-7.41\pm0.85$&
0.69&
&
&
\tabularnewline
&
2004-May-17&
43.6108024&
$-6.94\pm1.16$&
1.05&
$-7.18\pm1.44$&
$3.6\pm1.1$&
no\tabularnewline
USco 130&
2004-May-09&
35.7724090&
$-4.83\pm0.54$&
0.21&
&
&
\tabularnewline
&
2004-May-13&
39.8538830&
$-4.95\pm0.74$&
0.55&
$-4.89\pm0.92$&
$15.2\pm1.1$&
no\tabularnewline
USco 132&
2004-May-13&
39.8268683&
$-7.18\pm0.58$&
0.30&
&
&
\tabularnewline
&
2004-May-17&
43.6391138&
$-7.37\pm1.02$&
0.89&
$-7.28\pm1.17$&
$9.1\pm0.7$&
no\tabularnewline
\hline
\end{tabular}

@@

\caption{Relative radial velocities (RVs) of objects measured in two
different epochs. The vertical axes indicate the amount of deviation
($\Delta \mathrm{RV}$) from the `average' radial velocitiy
($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}), and
the horizontal axes indicate the time of the observation in
heliocentric Julian date (HJD). The objects are considered to have a
non-constant RV when the error bars of two data points do not overlap
each other. The non-constant RV objects are considered as
binary/multiple candidates.}

@@

The radial velocities of each object were determined by using the cross-correlation
function of the object spectrum with that of a template star which has
a spectra type. By visual inspection,
the wavelength ranges used for the cross-correlation calculations
are chosen by avoiding the regions of spectra affected by the telluric
lines, and defects and fringes (in near infrared) of the CCDs. The
radial velocities of objects with respect to the template are obtained
by measuring the location of the peak in the cross-correlation function
which is fitted by a function which consists of two gaussian functions
(with a common centre) plus a constant term . LHS~49 (Proxima Cen, M5.5) was
chosen as the template for this purpose. The radial velocity of the
template object LHS~49 was obtained by measuring the wavelength shifts
of the prominent photospheric absorption features \ion{K}{i}~$\lambda\lambda$7664.911,~7698.974.
This gives us $\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$, which is
in good agreement with the earlier measurement of \citet{garcia-sanchez:2001}
who found $\mathrm{RV_{LHS49}=}-21.7\pm1.8\,\kmps$. The heliocentric
RV of each object can be then calculated by adding $\mathrm{RV_{LHS49}}$
with the RV of each object with respect to LHS~49. In the following
measurements of the heliocentric radial velocities, our measurement
($\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$) will be used for consistency.

@@

The result of the heliocentric RV measurements (from two epochs for
each object) is summarised in Table~\ref{tab:summary_results} along
with the uncertainties. The table also lists the uncertainties in
the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
is the uncertainty of RV with respect to the template star. The
two consecutive measurements of RVs (from same nights) are used to
find the (absolute/heliocentric) RV of the night, and their uncertainties are obtained from
the standard deviations of the mean ($\sigma_{\mathrm{RRV}}$) and
the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
Note that for finding a shift in the radial velocities from two
different epochs, only $\sigma_{\mathrm{RRV}}$ is important since one
only requires relative (with respect to a template) RV values.
The 'average' radial velocities ($\overline{\mathrm{RV}}$) of the
two epochs are also given in the same table. The $\overline{\mathrm{RV}}$
values of the objects in UScoOB are consistent with the earlier measurements
of \citet{muzerolle:2003} in Table~\ref{tab:literatures}, except
for the values for USco~66 and USco~75. This is unsurprising
since the former is a known binary \citep{kraus:2005} and the latter
is a non-constant RV object (a candidate for a multiple) found in
the RV-shift test which will be discussed next.

@@

We thank the staff of VLT of the ESO for the observations carried out in
service mode.  This work is supported by PPARC rolling grant PP/C501609/1.
